Solar wind prediction for the Solar Probe Plus orbit

### 2017-04-10 paperMVVB/sections/content.tex
optimized figs 3+8; build fig 9; drafted fig 10

\subsection{SSN correlation}
Our current interest lies in the correlation of the SSN to the solar wind median value, because it defines the position of the lognormal function. The yearly OMNI parameter medians and the yearly SSN are plotted in Fig.~\ref{fig:OMNI_yearly_ssn_correlation_b_plot}.\\

solar activity = SSN $\neq$ solar cycle\\
The solar wind velocity (and its close friends N \& T) is known to depend on the state of the solar cycle (cite?), which is why it follows the SSN only indirectly (with time lag). Thus we derive the correlation coefficients for different time lags between solar wind parameters and SSN (see Fig.~\ref{fig:OMNI_yearly_ssn_correlation_b_plot}).\\
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/OMNI_yearly_ssn_correlation_b_plot.pdf}}
	\caption{Plot of the solar wind parameter yearly medians from OMNI data and the yearly SSN from the \citet{sidc} with cycle number (top). Their correlation coefficients with the yearly SSN for time lags back to -15 years (bottom).}
	\label{fig:OMNI_yearly_ssn_correlation_b_plot}
\end{figure}

@@

%SPP orbit
SPP orbit description, Venus flybys, within ecliptic, \citep{Fox2015}, (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_b_plot})\\

%SSN prediction
choosing SSN prediction sources as input:\\
SIDC prediction---12-month forecast (Kalman fiter combined method)\\
The SWPC prediction (until end of current cycle/end of 2019) follows a consensus of the Solar~Cycle~24 Prediction~Panel.\\
For the prediction of the next solar cycle we simply assume a course similar to the last and thus we simply shift the last cycle by 11~years. Additionally we consider the two alternatives of half and twice the amplitude.\\
SIDC + SWPC + previous cycle~24 (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_b_plot})\\
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_orbit_predicted_SSN_overview_b_plot.pdf}}
	\caption{SPP's solar distance during its mission time (top). Consecutive Venus flybys bring its perihelia nearer to the Sun. Actual and predicted SSN (bottom), i.e. SIDC 13-month smoothed monthly actual SSN, SIDC prediction, SWPC prediction and simply shifted SSN from previous cycle~24, together with two alternative trends of half and twice the amplitude.}
	\label{fig:SPP_orbit_predicted_SSN_overview_b_plot}
\end{figure}

Implementing the orbital distance data and predicted SSN for the mission time we get SPP's estimated solar wind environment.\\
A zoom into the first and the nearest perihelia shows... (Fig.~\ref{fig:SPP_perihelia_prediction_plot}).\\
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_plot.pdf}}
	\caption{Estimated B-field median during the first and nearest perihelia in 2018 and 2024.}
	\label{fig:SPP_perihelia_prediction_plot}
\end{figure}

\subsection{Near-Sun extrapolation behavior/effects}
The extrapolation distance is only about one third of the model range, but as the parameters follow exponential change, one has to look at the logarithmic distance which is indeed one and a half times the model range.\\

>>>>

\subsection{SSN correlation}
Our current interest lies in the correlation of the SSN to the solar wind median value, because it defines the position of the lognormal function. The yearly OMNI parameter medians and the yearly SSN are plotted in Fig.~\ref{fig:OMNI_yearly_ssn_correlation_c_plot}.\\

solar activity = SSN $\neq$ solar cycle\\
The solar wind velocity (and its close friends N \& T) is known to depend on the state of the solar cycle (cite?), which is why it follows the SSN only indirectly (with time lag). Thus we derive the correlation coefficients for different time lags between solar wind parameters and SSN (see Fig.~\ref{fig:OMNI_yearly_ssn_correlation_c_plot}).\\
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/OMNI_yearly_ssn_correlation_c_plot.pdf}}
	\caption{Plot of the solar wind parameter yearly medians from OMNI data and the yearly SSN from the \citet{sidc} with cycle number (top). Their correlation coefficients with the yearly SSN for time lags back to -15 years (bottom).}
	\label{fig:OMNI_yearly_ssn_correlation_c_plot}
\end{figure}

@@

%SPP orbit
SPP orbit description, Venus flybys, within ecliptic, \citep{Fox2015}, (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_c_plot})\\

%SSN prediction
choosing SSN prediction sources as input:\\
SIDC prediction---12-month forecast (Kalman fiter combined method)\\
The SWPC prediction (until end of current cycle/end of 2019) follows a consensus of the Solar~Cycle~24 Prediction~Panel.\\
For the prediction of the next solar cycle we simply assume a course similar to the last and thus we simply shift the last cycle by 11~years. Additionally we consider the two alternatives of half and twice the amplitude.\\
SIDC + SWPC + previous cycle~24 (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_c_plot})\\
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_orbit_predicted_SSN_overview_c_plot.pdf}}
	\caption{SPP's solar distance during its mission time (top). Consecutive Venus flybys bring its perihelia nearer to the Sun. Actual and predicted SSN (bottom), i.e. SIDC 13-month smoothed monthly actual SSN, SIDC prediction, SWPC prediction and simply shifted SSN from previous cycle~24, together with two alternative trends of half and twice the amplitude.}
	\label{fig:SPP_orbit_predicted_SSN_overview_c_plot}
\end{figure}

Implementing the orbital distance data and predicted SSN for the mission time we get SPP's estimated solar wind environment.\\
A zoom into the first and the nearest perihelia shows... (Figs.~\ref{fig:SPP_perihelia_prediction_c_plot} and \ref{fig:SPP_perihelia_prediction_nearest_c_plot}).\\
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_c_plot.pdf}}
	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during SPP's first perihelion in 2018. For the velocity slow and fast part are plotted.}
	\label{fig:SPP_perihelia_prediction_c_plot}
\end{figure}
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_nearest_c_plot.pdf}}
	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during SPP's nearest perihelion in 2024. For the velocity slow and fast part are plotted.}
	\label{fig:SPP_perihelia_prediction_nearest_c_plot}
\end{figure}
\subsection{Near-Sun extrapolation behavior/effects}
The extrapolation distance is only about one third of the model range, but as the parameters follow exponential change, one has to look at the logarithmic distance which is indeed one and a half times the model range.\\
